\chapter{Conclusions}
\label{ch:con}
%AA Samenvatting Opdracht
For this project, we built a wireless monitoring system for Project MARCH. This system will be used to retrieve the data of the sensors inside the MARCH, an exoskeleton used for paraplegics to walk again.\\	
%BB Bevindingen project
We had to set up the wireless system from scratch since the system originally intended to handle the wireless turned out not to work correctly. This rerouted the focus of this project from data visualisation and rendering to setting up a wireless network and connecting it to Simulink, the module used for getting the signal data. In addition to setting up a wireless network, the data also had to be received and processed on the target computers. While developing the system we collaborated with the Project MARCH team by integrating their SCRUM planning with ours, joining their stand-ups, demo's and sprints.   \\
%CC Resultaat opdracht
On the receiving computers there were quite some performance issues as the rendering speed of the Matlab visuals were slower than initially expected. We also found out that the Simulink module had more limitations than we initially thought. Luckely, both issues were solved eventually. \\
%DD Voldoet aan opdracht
In the end, a system was created which was able to transfer data from a Simulink model which ran on the MARCH to a remote computer wirelessly. In addition, the GUI also runs smoothly. 
%EE Conclusie dat we shit hebben gehaald
\\ Considering the fact that all requirements save for two 'Would Have' have been achieved and even those are able to be implemented without much ado, we are lead to the conclusion that this project has been implemented successfully.  