\section{Data Processing}\label{sec:dataproc}
\subsection{Data Packaging}
The target update rate is 50 Hz. Some sensors might send data more often, it is not advised to send through all the sensor data separately as this can create a large amount of packets and a lot of overhead. This will congest the wireless connection, which will lead to sensor failing to make the target rate. It is more efficient to collect the data and send it through at the set rate of 50 Hz. This will minimize the overhead, as only the lowest amount of needed packets will be send to the receiver.

The matrix that will collect the data will be a n x m matrix, where n is the amount of sensors and m is the amount of columns defined. Currently the following columns have been defined:\\
\begin{enumerate}
	\item Sensor label
	\item Sensor type
	\item Sensor data
	\item Changed since last packet
\end{enumerate}
If a sensor sends it's data to the master, the corresponding `Sensor data'-value in the matrix will be updated and the column `Changed since last packet' will be set to `1'. Only the rows for which applies that `Changed since last packet' $==$ `1' will be added to the UDP packet that is send over to the receiver. After a packet has been sent, every value in the `Changed since last packet'-column gets reset back to `0'.

The maximum data size for a UDP-packet in Matlab is `64k' or 65,536 bytes. The size of a double-value is 64 bits. Currently the exoskeleton has 47 sensors. To show that the matrix is scalable, let's take an example in which the exoskeleton has been upgraded to 100 sensors and there has been defined an extra column. The total data size will be $(100*5*64) = 32000$ bits $= 4000$ bytes which is still more than 16 times lower than the size limit. 

\subsection{Converting Raw Data}
%TODO Correcte weergave data vs snel weergave data